\documentclass[sigconf]{acmart}

\fancyhf{} % Remove fancy page headers                                          
%\fancyhead[C]{Anonymous submission \#83 to ACSAC 2017}                                            
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions              

%\acmConference[Anonymous Submission to ACSAC 2017]{2017 Annual Computer Security Applications Conference}{Due 8 June 2017}{San Juan, Puerto Rico, USA}
\acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions                                                        


\input{preamble.tex}
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\sffamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


\begin{document}

\title{Decentralized Certificate Authorities}


\author{Bargav Jayaraman, Hannah Li, David Evans}
\authornote{The first two authors both contributed as co-equal first authors.}
\affiliation{\institution{University of Virginia}
\city{\href{https://oblivc.org/dca}{\sf https://oblivc.org/dca}}}
\email{[bargavj, hannahli, evans]@virginia.edu}

\begin{abstract}
\label{sec:abstract}
The security of TLS depends on trust in certificate authorities, and
that trust stems from their ability to protect and control the use of
a private signing key.  The signing key is the key asset of a
certificate authority (CA), and its value is based on trust in the
corresponding public key which is primarily distributed by browser
vendors.  Compromise of a CA private key represents a single
point-of-failure that could have disastrous consequences, so CAs go to
great lengths to attempt to protect and control the use of their
private keys. Nevertheless, keys are sometimes compromised and may be
misused accidentally or intentionally by insiders. We propose a new model where a CA's private key is split among
multiple parties, and signatures are produced using a secure
multi-party computation protocol that never exposes the actual signing
key. This could be used by a single CA to reduce the risk that its
signing key would be compromised or misused. It could also enable new
models for certificate generation, where multiple CAs would need to
agree and cooperate before a new certificate can be generated, or even
where certificate generation would require cooperation between a CA
and the certificate recipient (subject). We demonstrate the
practicality of this concept with an evaluation of a prototype
implementation that uses secure two-party computation to generate
certificates signed using ECDSA on curve secp192k1. We show that using
Amazon AWS EC2 c4.2xlarge nodes to jointly sign a certificate costs as
little as 28.2-32.6 cents without bandwidth cost and approximately
8.54 dollars with bandwidth cost.
 
   
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%


\keywords{Certificate authority, TLS, secure multi-party computation, MPC}


\maketitle

\input{01_introduction}
\input{02_background}
\input{03_design}
\input{04_implementation}
\input{05_performance}
%\input{security}
\input{06_discussion}
\input{07_related}
\input{08_conclusion}

\subsection*{Availability}

Our code is available under an open source license from:
\begin{center}
\url{https://github.com/hainali/decentralizedca}.
\end{center}

\begin{acks}
The authors thank Jack Doerner for providing the Absentminded Crypto Kit and extensive help with using it, and Samee Zahur for developing and supporting Obliv-C.  The work was partially funded by an award from the National Science Foundation (1111781) and gifts from Amazon, Google, and Microsoft.
\end{acks}

\appendix

\input{appendix}

\clearpage

\bibliographystyle{ACM-Reference-Format}
\makeatletter
\def\url@bibstyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\scriptsize\sffamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{bib}

\bibliography{decentralized_ca}

\end{document}
